Agreement Attraction

### 2019-06-10 Paper/AgreementAttraction.tex
almost a mediocre paper

\documentclass[doc]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes},
            pdfauthor={Utku Türk~\& Pavel Logačev},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
Morphemes}
    \author{Utku Türk\textsuperscript{1}~\& Pavel Logačev\textsuperscript{1}}
    \date{}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{xcolor}
\usepackage{hhline}
\usepackage{mathtools}
\usepackage{gb4e}\noautomath

\authornote{Add complete departmental affiliations for each
author here. Each new line herein must be indented, like this line.
Enter author note here.

Correspondence concerning this article should be addressed to Utku Türk,
Postal address. E-mail:
\href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}}

\abstract{
This paper deals with agreement attraction because it's more important
than literally anything else. Recently, Lago et al. (2018) demonstrated
agreement attraction effects in comprension in Turkish, which is
super-interesting because this finding allows us to make a lot of money.
However, there is an alternative explanation for their findings: dark
sorcery. In this paper we tested the predictions of these alternative
accounts. In Experiment 1, we found that a particular kind of dark
sorcery was not involved. In Experiment 2, we shall find \ldots{}

@@

\section{INTRODUCTION}\label{introduction}

Attraction errors in the production and comprehension of subject-verb
agreement, in which a verb does not agree with the grammatical agreement
controller, but with a potential attractor, have been the main topic of
research in many studies for quite a long time. In fact, it is still a
widely researched area in psycholinguistic studies. Despite the
comprehensive research that has been carried out, studies that have been
conducted on agreement attraction in Turkish have been very limited. In
fact, Lago (2018) is currently the only study that explores this
phenomenon in Turkish. Lago (2018) makes use of genitive-possessive
structures in the subject position, in which the possessive-marked noun
is the head of the noun phrase which acts as the grammatical agreement
controller, and the genitive noun serves as a potential attractor. In a
speeded acceptability judgment study, Lago (2018) found a significant
effect of number agreement attraction. However, the interpretation of
their findings may be a result of the fact that non-subjecthood cues
originate from their use of morphologically ambiguous forms of the
possessive. In the possessive forms that are used, all the head nouns in
their stimuli are ambigiuous between possessive and accusative.

In Turkish, accusative number agreement controllers are extremely rare,
while genitive agreement controllers are very frequent. Thus, Lago
(2018)'s finding could potentially be explained with occasional shallow
processing. When all syntactic relations in the sentence were processed
fully, the possessive noun may have been identified as the controller.
Meanwhile, the genitive noun may sometimes have been erroneously
identified as the controller during shallow processing because genitives
are more likely to act as agreement controllers than accusatives
(SOURCE). A second alternative explanation for Lago (2018)'s findings
may be the fact that participants may engage in even more shallow
processing than outlined above. Participants may have erroneously
responded \emph{Yes} on some trials for two main reasons: (i) the
presence of a plural morpheme on a noun (attractor or controller), and
(ii) the presence of a plural agreement morpheme on the verb. We
speculate that in such trials, participants would have simply tried to
check for the presence of such morphemes, while largely disregarding the
remainder of the sentence.

We first replicated Lago (2018)'s experiment with unambiguous head
nouns. To this end, we revised the items that were used previously in
order to avoid morphological ambiguity between possessive and accusative
forms. The effect found in Lago (2018) was also observed when
unambiguous nouns were used, as will be discussed in \S 2.

\S 3 discusses the alternative account that posits even more shallow
processing as mentioned above and presents a pre-registered experiment
using RC attractors with potential outcomes and their indications. Since
both nominal and verbal plural morphemes in Turkish are expressed with
the same form (\emph{-ler} or \emph{-lar} depending on the phonological
environment), we can test this possibility with an experiment in which a
relative clause with or without plural agreement on the verb in place of
the genitive possessors is used. An agreement attraction effect similar
in magnitude to that observed in Lago (2018) would indicate that
participants use the aforementioned strategies.

\S 4 offers a discussion of the issue of number attraction and where
this experiments leaves us. Lastly, \S 5 presents a brief conclusion and
topics for future research.

\section{Experiment 1}\label{experiment-1}

In their study, Lago (2018) investigates the comprehension of
subject-verb agreement Turkish monolinguals. They use speeded
acceptability judgments for the effects of number attraction in Turkish.
Their sentences make us of genitive-possessive constructions in the
subject position, where the genitive is the attractor and the possessive
is the head noun. They manipulate the grammaticality of the sentence by
changing the plural morphology of the verb, and they also manipulate the
plurality of the attractor noun. In grammatical conditions, the subject
and the verb both bear singular morphology with no overt morpheme.
Moreover, in the ungrammatical conditions, the verb bears the overt
\emph{-lAr} morpheme whereas the subject is still singular as
exemplified below.

@@

They found a significant effect of number attraction in Turkish ranging
between 11\%--15\% across monolinguals. As seen in the results of the
statistical analysis in \textsc{Table} (\ref{lagomodel}), the
acceptability judgments showed an immense effect of grammaticality, and
there is also interaction between grammaticality and attractor number,
which indicates the presence of a number attraction effect.

\begin{table}[!hbt]
\centering
\begin{tabular}{llcccc}
\hline
    &                                        & \multicolumn{4}{l}{Monolingual Speakers}                                               \\ \cline{3-6} 
    &                                        & $\beta$        & SE            & \emph{z} & \emph{p} \\ \hline
\multicolumn{2}{l}{\textbf{Attraction Task}} &                &               &                           &                           \\
    & Grammaticality                         & \textbf{-5.51} & \textbf{0.33} & \textbf{-16.69}           & \textbf{.000}             \\
    & Attractor Number                       & 0.14           & 0.25          & 0.57                      & .571                      \\
    & Grammaticality x Attractor Number      & \textbf{1.69}  & \textbf{0.53} & \textbf{3.19}             & \textbf{.001}             \\
    & Attractor Number: Ungram conditions    & \textbf{0.94}  & \textbf{0.26} & \textbf{3.68}             & \textbf{.000}             \\
    & Attractor Number: Gram conditions      & -0.79          & 0.52          & -1.51                     & .131                      \\ \hline
\end{tabular}
\caption{Model results for the judgments of monolingual cited from @Lago.}
\label{lagomodel}
\end{table}

Lago (2018) stipulate that the Turkish genitive case does not provide a
strong cue against subjecthood since Turkish frequently makes use of
genitive marked subjects in embedded clauses, as in example
(\ref{gensubj}). This is in contrast with English, in which the genitive
case is compatible with subjecthood. Thus, Lago (2018) argue that this
robust agreement attraction effect has been linked to the case
information carried by accusative and genitive.

@@

All of our data, experimental materials, our experiment design, and our
fillers can be found on the website of the Center for Open Science
Framework (\url{https://osf.io/}).

>>>>

\documentclass[doc]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Agreement Attraction},
            pdfauthor={Utku Türk~\& Pavel Logacev},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{biblatex}
\ExecuteBibliographyOptions{maxbibnames=999}
\addbibresource{myreferences.bib}
\addbibresource{r-references.bib}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Agreement Attraction}
    \author{Utku Türk\textsuperscript{1}~\& Pavel Logacev\textsuperscript{1}}
    \date{}

\shorttitle{Agreement Attraction in Turkish}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Boğaziçi University}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{hhline}
\usepackage{mathtools}
\linespread{1}
\usepackage{gb4e}
\noautomath
\usepackage{setspace}
\makeatletter
\apptocmd{\@exe}{\singlespacing}{}{}
\makeatother
\usepackage{sectsty}
\allsectionsfont{\large}
\usepackage{color}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue}
\usepackage[english]{babel}
\addto\extrasenglish{\renewcommand{\itemautorefname}{Item}}
\renewcommand*{\nameyeardelim}{\addcomma\space}
\usepackage{tikz}
\usepackage{tikz-qtree}
\let\eachwordone=\textit

\authornote{

Correspondence concerning this article should be addressed to Utku Türk, . E-mail: \href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}}

\abstract{
The comprehension of agreement within the elements of a sentence is known to fail. One of these comprehension errors is known as agreement attraction. Speakers may erroneously find a sentence in which the ``attractor'' agrees with the verb instead of the ``head'' of the subject. Data from typologically different languages and explanations from different frameworks shows that we are far from understanding by what the attraction is modulated. Some theories refer this phenomenon as a faulty representation of the number on the head of the subject phase whereas other theories argues that the attraction is due to an error in the access to the number of the subject. In this paper, we report two experiments exploring a possible explanation for agreement attraction: an extremely shallow processing. The first experiment is a replication of \textcite{Lago2018} where we changed the head of the subject in order to differentiate between the accusative case \emph{-I}. In the second experiment, we have used a relative clause which only consists of a plural marked verb as a distractor. Our results show that while people do indeed care more than just ``matching'' the forms of plural verbal. Either comprehenders have some sort of restriction to not use cues from verbs upon accessing the number of the plural morpheme or there is a syntactic reason for the number feature of plural morpheme to not ``percolate.''

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{literature}{%
\section{Literature}\label{literature}}

\hypertarget{theories-of-attraction}{%
\subsection{Theories of attraction}\label{theories-of-attraction}}

Agreement attractions are defined as instances of incorrect agreements of an element with a distractor that is not its grammatical controller. As in \autoref{E1}, the target of the agreement is the verb \emph{are}, the attracting distractor is \emph{bottles}, and the feature erroneously assesed is the number feature of the grammatical controller \emph{label}.

\begin{exe}
\ex[*]{The label on the bottles \textit{are} wrong.\footnotemark}
\label{E1}
\end{exe}

\footnotetext{The convention of using $\ast$ is to show the ungrammaticality of the sentencee.}

This type of attraction, called number attraction in subject-verb agreement, first theorized by \textcite{Quirk1972} and attested experimentally by \textcite{Bock1991} in language production. One of the theoretical attempts to explain such phenomenon was Marking and Morphing Theories \autocites{Bock2001}[ among others]{Eberhard2005}. The reason it is called \emph{Marking} and \emph{Morphing} is because there is two possible explanation within the framework with regards to where and when the attraction occurs. First possibility is speaker (and/or comprehender) can erroneously create a semantic representation of the head with wrong number feature in the marking process in the marking process. Another possibility is that the attraction may arise from an interfering number feature of the attractor with the number feature of the highest noun phrase node in morphing process. During the this process, the speaker forms a final number value of the subject phrase, which is determined by each morpheme within the same phrase and their number information with particular weight. In morphing process, these other morphemes with number information may contaminate the final number value with perculation mechanism, which depends on the depth of the syntactic embedding. As the prediction goes, the more embedded an attractor is, the less attraction they trigger as shown in \textcite{Bock1992} in which authors shown that attractors within a relative clause trigger less agreement attraction in the production.

However, other studies shown that other preverbal elements, such as objects, object relative clauses, object clefts, and object questions, may trigger agreement attraction \autocites{Kimball1971}{Hartsuiker2001}{Franck2006}[ among others]{Franck2015}. In sentences like \autoref{E2}, the pronominal object \emph{hen} triggers and agreement attraction without being a part of the subject.

\begin{exe}
\ex[*]{
\gll Theo denkt dat de knecht hen roep.\\
Theo thinks that the servant them call.\textsc{Pl}.\\
\trans  `Theo thinks that the servant \textit{call} them'}
\label{E2}
\end{exe}

Since the Marking and Morphing theories put the source of the agreement attraction on the probe, i.e.~subject phrase, they cannot explain agreement attraction effects that are triggered by an distractor outside of the syntactic scope of the subject. Regardless, these effects can be explained in a framework where the source of the agreement attraction can placed on the trigger, i.e.~verb. \textcite{Badecker2007} suggests that a process where the subject is retrieved from the memory plays a role in agreement attraction effects as well \autocite[see as well][]{Wagers2009}. Building on the work in cue-based retrieval mechanism \autocites{Gordon2001}{Lewis2005}[ among others]{Lewis2006}, they argued that when spakers reach the verb, they try to retrieve the subject using certain features (cues) that essentially marks the \emph{subjecthood}. Thus, any element that matches (or partially mathces) with the cues in use may cause agreement attraction regardless of their position or syntactic relation to the subject. Going back to \autoref{E2}, it is expected, then, for an object which shares features like being preverbal, being a noun phrase, ability to bear agreement with a subject to trigger agreement attraction.

Another challenge for the Marking and Morphing model was the grammaticality asymmetry. Due to the spreading activation formula utilized in the Marking and Morphing model \autocite[see][]{Dell1986}, this model overgeneralizes the attraction effects to both ungrammatical and grammatical sentences and predicts both \autoref{E1} and \autoref{E3} to be present empirically, which is not the case \autocite{Wagers2009}.

\begin{exe}
\ex[*]{The labels on the bottle \textit{is} wrong.}
\label{E3}
\end{exe}

On the other hand, cue-based retrieval models successfully predicts the the grammaticality asymmetry as shown by \textcite{Dillon2013} in an ACT-R simulation as well as numerous studies in self-paced reading, eye-tracking, and ERP studies \autocites{Wagers2009}{Tucker2010}{Tanner2014}[ among others]{Lago2015}. This success was due to their replacement of source of the attraction. According to cue-based retrieval models, the probe, verb, presents certain cues to retrieve an NP with matching features in agreement. When features of the grammatical controller of the verb does not \emph{fully} match with the cues, no single NP will be satisfying the \emph{agreement}. Thus, another NP in the clause can match with cues presented by the VP, such as its case, syntactic position, grammatical number. Thus, if there is no \emph{retrieval cue} in the first place, i.e.~the verb is nor marked plural, there will be no need for partial match.

\hypertarget{turkish-relative-clauses-and-plural-marking}{%
\subsection{Turkish relative clauses and plural marking}\label{turkish-relative-clauses-and-plural-marking}}

Before discussing the experiments, we will touch upon the mechanisms that we utilize in the experiments: optional plural agreement, relative clause structure, and syncretism between possessive and accusative.

Turkish plural agreement is quite similar with regards to the subject-verb number agreement in the first and second plural person. However, Turkish plural agreement is optional in third person plurals as shown in \autoref{TB1} and \autoref{TB2}. The other characteristics of Turkish plural agreement is that, the nominal and verbal plural marking is done by the same morpheme \emph{-lAr}\footnote{The convention of using an uppercase A is to show that the morpheme can surface as either \textit{-ler} or \textit{-lar} according to the previous vowel due to the vowel harmony reasons.}.

\begin{exe}
\ex \label{TB1} Dün çocuk-\textsc{Lar} okul-a git-ti-\textsc{Ler} mi?
\ex 
\gll Dün çocuk-LAR okul-a git-ti mi?\\
yesterday child-\textsc{Pl} school-\textsc{Dat} go-\textsc{Pst}(-\textsc{Pl}) Q\\
\trans ``Did the children go to school yesterday?''
\label{TB2}
\end{exe}

As for Turkish relative clauses, they always precede the external head noun \autocites{Goksel2004}{Taylan2015} and they use either \emph{-An} or \emph{-dIk} nomilizers to show the referentiality of the subject within the relative clause as shown in \autoref{TB3} and \autoref{TB4} \autocite{Haig1997}. Moreover, due to pro-drop and null object properties of the Turkish \autocite[see][]{Ozturk2005}, relative clauses can consist of only the verb itself in Turkish as in \autoref{TB5}.

\begin{exe}
\ex \label{TB3}
\gll Kazı-lar-ın yap-ıl-dığ-ı alan ... \\
excavation-\textsc{Pl}-\textsc{Gen} do-\textsc{Pass}-\textsc{Nmlz}-\textsc{Poss} area ... \\
\glt ``The place where the excavations are done ...''
\ex \label{TB4}
\gll Kazı-lar yap-ıl-an alan ... \\
excavation-\textsc{Pl} do-\textsc{Pass}-\textsc{Nmlz} area ... \\
\glt ``A place where some excavations are done ...''
\ex \label{TB5}
\gll Gör-düğ-ü kuş çok güzel-di.\\
see-\textsc{Nmlz}-\textsc{Poss} bird very pretty-\textsc{Pst}\\
\glt ``The bird that he/she saw was very pretty.''
\end{exe}

Final characteristics that interests us in this paper is the morphological syncretism between the accusative case and possessive suffix in Turkish. When the possessive case is attached to a nominal stem that ends with a consonant, it is pronounced as \textit{-I}, which is exactly how accusative case is also pronounced in the same environment in Turkish. However, the ambiguity is immediately resolved when they follow a nominal stem that ends with a vowel. In the latter environment, the accussative case surfaces as \emph{-yI} whereas the possessive surfaces as \emph{-sI(n)}\footnote{The final \textit{n} is only surfaces when any other morphemes follows the possessive suffix. Otherwise, it surfaces as \textit{-sI}} as shown in \autoref{TB6}-\autoref{TB9}.

\begin{exe}
\ex
\begin{xlist}
\ex \label{TB6}
\gll Kuş-\textbf{u} beğen-di-m.\\
bird-\textsc{Acc} like-\textsc{Pst}-\textsc{1Sg}\\
\glt ``I liked the bird.''
\ex \label{TB7}
\gll Emin'in kuş-\textbf{u} güzel-miş.\\
Emin-\textsc{Gen} bird-\textsc{Poss} pretty-\textsc{Evd}\\
\glt ``Emin's bird was pretty.''
\ex \label{TB8}
\gll Kedi-\textbf{yi} beğen-di-m.\\
cat-\textsc{Acc} like-\textsc{Pst}-\textsc{1Sg}\\
\glt ``I liked the cat.''
\ex \label{TB9}
\gll Emin'in kedi-\textbf{si} güzel-miş.\\
Emin-\textsc{Gen} cat-\textsc{Poss} pretty-\textsc{Evd}\\
\glt ``Emin's cat was pretty.''
\end{xlist}
\end{exe}

\hypertarget{the-current-study}{%
\section{The Current Study}\label{the-current-study}}

In this study, we examine the question of whether agreement attraction is due to the shallow parsing that mainly depends on the memory of plural morpheme \emph{-lAr} and matching the verbal plural morpheme with the nominal plural morpheme.

First of all, we investigate the effects of ambiguous suffix with Experiment 1, which is a replication of \textcite{Lago2018}. \textcite{Lago2018} makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor as in \autoref{Lagoitem}. In a speeded acceptability judgment study, \textcite{Lago2018} found a significant effect of number agreement attraction. However, the interpretation of their findings may be a result of the fact that non-subjecthood cues originate from their use of morphologically ambiguous forms of the possessive. In the possessive forms that are used, all the head nouns in their stimuli are ambigiuous between possessive and accusative.

\begin{exe}
\ex \label{Lagoitem}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{Gen} vocalist-\textsc{Poss} stage-\textsc{Loc} non-stop jump-\textsc{Pst}-\textsc{3Pl}\\
\glt The singer's backup vocalist jumped on the stage non-stop.
\end{exe}

In Turkish, accusative number agreement controllers are extremely rare, while genitive agreement controllers are very frequent. Thus, \textcite{Lago2018}'s finding could potentially be explained with occasional shallow processing. When all syntactic relations in the sentence were processed fully, the possessive noun may have been identified as the controller. Meanwhile, the genitive noun may sometimes have been erroneously identified as the controller during shallow processing because genitives are more likely to act as agreement controllers than accusatives. In order to check this effect, we have replicated \textcite{Lago2018} in Experiment 1. We have used different head nouns which ends with a vowel to differentiate between the accusative case and the possessive suffix, i.e. \emph{taksici} (taxi driver) instead of \emph{vokalist} in \autoref{Lagoitem}.

With regards to percolation theories, this replication should yield no difference from \textcite{Lago2018}. The syntactic depth has not changed, the number information of the head and distractor have not changed. Slight differences may be expected since we have changed some items which can be found in Appendix 1, and this situation can create a erroneous number information to be used in the marking process.

As for cue-based retrieval models, we should expect a lower agreement attraction effect in this replication. This predictions stems from the fact that possibility of erroneous representation of features of head noun is now lower due to our efforts to differentiate between the accusative case and the possessive marking. \textcite{Lago2018} argues that due to the subjecthood information provided by genitive case, there is an effect of agreement attraction. We eliminate the possibility of possible non-subjecthood clues given by the form that is shared by the accusative case and the posessive suffix.

Within the shallow processing model, we would also expect a no change in the status of agreement attraction. In our account of shallow processing, we argue that when the comprehenders reach the verb and saw plural morpheme, they engage in matching mechanism where they try to match the verbal plural morpheme with a previous nomimal plural morpheme. An agreement attraction, then, is not a result of a partial matching or a representational error of number feature; instead, it is the result of a state of memory in which comprehenders misremember either the existence of the nominal plural morpheme or the place of the nominal plural morpheme as stated in the MPT model of the agreement attraction within shallow processor within \autoref{model1}, \autoref{model2}, \autoref{model3}\footnote{Author here wishes he knew more latex to do the MPT tree more neat.}.

\begin{figure}[htb!]
\centering
\begin{tikzpicture}[
    sibling distance        = 0.5em,
    level distance          = 5em,
    edge from parent/.style = {draw, -latex},
    every node/.style       = {font=\scriptsize},
    sloped
  ]
\Tree [.{\ }
        \edge node[auto=left]{f}; [.\node[draw,rounded corners=.8ex]{generic failure};
                                     \node[draw]{Ungrammatical};]
        \edge node[auto=left]{1-f};
        [.\node[draw,rounded corners=.8ex]{no failure};
          \edge[dashed]; [.\node[]{Plural Verbs}; 
                           \edge[dashed]; \node[]{With Distractor};
                           \edge[dashed]; \node[]{Without Distractor};
                         ] 
          \edge[dashed]; [.\node[]{Singular Verbs}; 
                          \edge[dashed]; [.\node[draw,rounded corners=.8ex]{No checking};
                                           \node[draw]{Grammatical};]
                         ] 
        ] 
      ]
\end{tikzpicture}
\caption{xd}
\label{model1}
\end{figure}

\begin{figure}[htb!]
\centering
\begin{tikzpicture}[
    sibling distance        = 0.5em,
    level distance          = 5em,
    edge from parent/.style = {draw, -latex},
    every node/.style       = {font=\scriptsize},
    sloped
  ]
\Tree [.\node[]{Without Distractor}; 
                                          \edge node[auto=left]{m$_2$}; [.\node[draw,rounded corners=.8ex]{No Memory of -lAr};
                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
                                          \edge node[auto=left]{1-m$_2$}; [.\node[draw,rounded corners=.8ex]{Memory of -lAr}; 
                                          \edge node[auto=left]{1-p$_2$}; [.\node[draw,rounded corners=.8ex]{No Place of -lAr};
                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
                                          \edge node[auto=left]{p$_2$}; [.\node[draw,rounded corners=.8ex]{Misrepresented place of -lAr};
                                                                        \node[draw]{Ungrammatical};]]]

\end{tikzpicture}
\caption{xd}
\label{model2}
\end{figure}
\begin{figure}[htb!]
\centering
\begin{tikzpicture}[
    sibling distance        = 0.5em,
    level distance          = 5em,
    edge from parent/.style = {draw, -latex},
    every node/.style       = {font=\scriptsize},
    sloped
  ]
\Tree [.\node[]{With Distractor}; 
                                          \edge node[auto=left]{m$_1$}; [.\node[draw,rounded corners=.8ex]{No Memory of -lAr};
                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
                                          \edge node[auto=left]{1-m$_1$}; [.\node[draw,rounded corners=.8ex]{Memory of -lAr}; 
                                          \edge node[auto=left]{1-p$_1$}; [.\node[draw,rounded corners=.8ex]{No Place of -lAr};
                                                                        \edge node[auto=left]{g}; \node[draw]{Grammatical};
                                                                        \edge node[auto=left]{1-g}; \node[draw]{Ungrammatical};]
                                          \edge node[auto=left]{p$_1$}; [.\node[draw,rounded corners=.8ex]{Memory of place of -lAr};
                                                                        \node[draw]{Grammatical};]]]

\end{tikzpicture}
\caption{xd}
\label{model3}
\end{figure}

In our second experiment, we investigate the predictions made from our model using a verbal plural morpheme within a distractor relative clause. As mentioned earlier, the verbal plural morpheme in Turkish is exactly the same with the nominal plural with regards to its stress, its behaviour, and its form: \emph{-lAr}. Since Turkish relative clauses are essentially nominals due the nomilization process, they behave exactly like other nominals within the sentence \autocites{Goksel2004}{Taylan2015}. They can be marked with cases, plural agreement and they can have postpositions that any nominal also can. This syntactic formation enables us to question how shallow people process, how much syntactic information is relevant, or how perfectly people encode the features of the elements of the sentence. In our experiment 2, we have used items in which the referential head noun of the subject is modified with a single-word relative clause as in \autoref{ouritem1}.

\begin{exe}
  \ex \label{ouritem1}
      \gll D\"{o}v-d\"{u}k-(\textbf{ler})-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-(\textbf{lar})-d{\i}.\\
  beat-\textsc{Nmlz}-(\textsc{Pl})-\textsc{Poss} kid kitchen-\textsc{Loc} unconscious state-\textsc{Loc} lie-\textsc{Prog}-(\textsc{Pl})-\textsc{Pst}\\
      \glt Intended: The kid that they beat were laying in the kitchen unconscious.
\end{exe}

Within the framework of percolation theories, we expect a harsh decline in the agreement attraction effects\footnote{Discussion regarding to the how and where relative clauses adjoined is omited due to the scope of the paper. However, it should be clear that a late insertion analysis where the relative clauses are actually above the head noun would yield different results. In this paper, I assume that modifiers like relative clauses are within the noun phrase, which deems them \textit{syntactically} deeper placed in the hierarchical three than the possessee.}. The reason for this expected decline is the fact that relative clauses being relative \emph{deeper} in the hierarchical structure than the possessee of genitive-posessive structure.

As for cue-based retrieval models, we would expect an agreement attraction quite similar to the one that we originally have in \textcite{Lago2018}. The reason for this expected agreement attraction is the fact that apart from having a verbal root, the relative clauses and nomials are behave exactly the same in terms of \emph{nounnness}. Like nominals, nominalized structures first marked with plural and then with the case or possessive suffix. From this aspective, it seems like there should be no difference. However, one may argue that the features related to the verbal and nominal can be encoded differently. Thus, there will no partial match at any time given due to the fact that verbal plural morpheme at the main verb does specify cues for specific type of plural marking. One other question that may arise from this structure is that whether or not the parts of already-formed dependencies can feed the following dependency resolution. In other words, the verbal plural morpheme \emph{-lar} on \emph{dövdükleri} in \autoref{ouritem1} is already a trigger of a cue retrieval process. And, when it is merged with the nominal head \emph{çocuk}, there is a formed semantic meaning that is \enquote{a group of people have beaten a kid.} However, this \emph{suggesstion} assumes that relative clauses are formed at the very moment. Moreover, we also need to assume that after forming a relative clause they are unreachable, meaning that they do not contribute to the processing of the sentnece, anymore.

Lastly in our extremely shallow processing model, we would expect a significant effect of agreement attraction. Due to one of the writers inability to \emph{run the numbers} and \emph{form the mpt trees in time}, this part unfortunately does not go beyond than a verbal argumentation. The reason we wait a significant effect of agreement is due to the fact that upon the agreement process is driven by the faulty memory of the place of the plural morpheme and uneducated guessing. Since the parsing is shallow, comprehenders do not engage in perfect attribution of the features, thus having a somewhat blurry representation behind. We expect for this behaviour to be omnipresent in other agreement attraction phenomenon that has been showed, as well as in \textcite{Lago2018} and in our replication of it. Therefore, there is no reason to have to anything to be different in experiment 2.

\hypertarget{experiment-1}{%
\subsection{Experiment 1}\label{experiment-1}}

In their study, \textcite{Lago2018} investigates the comprehension of subject-verb agreement Turkish monolinguals. They use speeded acceptability judgments for the effects of number attraction in Turkish. Their sentences make us of genitive-possessive constructions in the subject position, where the genitive is the attractor and the possessive is the head noun. They manipulate the grammaticality of the sentence by changing the plural morphology of the verb, and they also manipulate the plurality of the attractor noun. In grammatical conditions, the subject and the verb both bear singular morphology with no overt morpheme. Moreover, in the ungrammatical conditions, the verb bears the overt \emph{-lAr} morpheme whereas the subject is still singular as exemplified below.

@@

They found a significant effect of number attraction in Turkish ranging between 11\%--15\% across monolinguals. \textcite{Lago2018} stipulate that the Turkish genitive case does not provide a strong cue against subjecthood since Turkish frequently makes use of genitive marked subjects in embedded clauses, as in \autoref{gensubj}. This is in contrast with English, in which the genitive case is compatible with subjecthood. Thus, \textcite{Lago2018} argue that this robust agreement attraction effect has been linked to the case information carried by accusative and genitive.

@@

\hypertarget{participants-and-procedure}{%
\subsubsection{Participants and Procedure}\label{participants-and-procedure}}
